\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{appendix}

% Include other packages here, before hyperref.

% for using the same institution for all three authors
\usepackage{authblk}
% for the ä in Universität
\usepackage[utf8]{inputenc}

\usepackage{subcaption}

% tables
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{nicefrac}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{xargs}                      % Use more than one optional parameter in a new commands
\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
\usepackage[colorinlistoftodos,textsize=small]{todonotes}
\newcommandx{\todoc}[2][1=]{\todo[linecolor=orange,backgroundcolor=orange!25,bordercolor=orange,#1]{TODO: #2}}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{UNSURE: #2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{CHANGE: #2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{INFO: #2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{IMPROVEMENT: #2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{THIS WILL NOT SHOW: #2}}
\setlength{\marginparwidth}{2cm}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
% The following line needs to be commented out if one wants page-number in final publication mode
%\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{Unsupervised Monocular Depth Estimation Using Atrous Convolutions}

\author{Fabian Kessler}
\author{Steven Lang}
\author{Dominik Straub}

\affil{Technische Universität Darmstadt \authorcr
  \{\tt firstname.lastname\}@stud.tu-darmstadt.de}

\maketitle
%\thispagestyle{empty}
%%%%%%%%% ABSTRACT
\begin{abstract}
Monocular depth estimation is concerned with computing a dense depth map from a single image but faces difficulties especially at object boundaries.
Atrous convolutions have been successfully employed to this end in the task of semantic segmentation.
In this paper, we investigate, whether it is  also possible to apply atrous convolutions in unsupervised monocular depth estimation. 
Specifically, we place an Atrous Spatial Pyramid Pooling block in a convolutional neural network between the encoder and decoder. 
This block allows for computing feature maps at different spatial scales on top of the encoder output. 
Our experiments show that atrous convolutions in the proposed setup do not improve depth estimation performance. 
Furthermore, the necessity of a lower output stride after the encoder, such that an increased receptive field size is even applicable, harms runtime and increases memory consumption. 
Finally, we show that it is possible to reduce the number of channels after the encoder, which reduces the parameter count without impairing predictions.
\end{abstract}
%%%%%%%%% BODY TEXT
%%%%%%%%% INTRO
\input{01-intro.tex}

%%%%%%%%% RELATED WORK
\input{02-related_work.tex}


%%%%%%%%% METHODS
\input{03-methods.tex}


%%%%%%%%% RESULTS
\input{04-results.tex}

%%%%%%%%% CONCLUSION
\input{05-conclusion.tex}

{\small
\bibliographystyle{ieee}
\bibliography{bibliography}
}

\clearpage
%%%%%%%%% APPENDICES
\input{06-appendix.tex}


\end{document}
